Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition

### 2015-07-17 papers/data_paper/ApJ_submission/datapaper.tex
submission day

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia}
\email{gsavorgn@astro.swin.edu.au}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{images/m49overlap.eps}
\caption{Example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{images/n4459nobrightstar.eps}
\caption{Example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
%\caption{the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

\begin{figure*}[h]
\begin{center}
\includegraphics[width=\fitfigurewidth]{images/n2974_1Dfit.eps}
\caption{Best-fit model, and isophotal parameters, for the galaxy NGC 2974. 
The left panels refer to the major-axis $R_{\rm maj}$, 
while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
The black points are the observed data.  
The color lines represent the individual (PSF-convolved) model components:
red=S\'ersic (bulge), dark blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
The best-fit parameters for the S\'ersic bulge model are inset.
The total (PSF-convolved) model is shown with a black dashed line, 
but it is hard to distinguish because it almost perfectly matches the data, 
hence the residual profile is additionally shown as $\Delta \mu$ in the second row.
The horizontal grey dashed line corresponds to an intensity 
equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. 
Such profiles are available online for all other galaxies successfully modelled in 1D (see Table \ref{tab:fitres}).}
\label{fig:n2974ex}
\end{center}
\end{figure*}

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
%\caption{the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
%\caption{the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
\caption{Image of the galaxy NGC 2974 with its mask (top panel), unsharp mask (second panel), 
best-fit 2D model (third panel), 
and residual image after the subtraction of the 2D model (bottom panel).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_r_e.eps} 
\caption{2D versus 1D major-axis measurements of the spheroid effective radii. 
The dashed line displays the 1:1 relation.}
\label{fig:re1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_n.eps} 
\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.}
\label{fig:n1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/comparison_mag.eps} 
\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ spheroid magnitudes. The dashed line displays the 1:1 relation.}
\label{fig:mag1d2d}
\end{center}
\end{figure}

@@

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
Each data point corresponds to an individual measurement from: 
\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
Black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to the measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively, 
corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres} (see Section \ref{sec:err} for details).
We consider these to be absolute upper limits to the uncertainty on our parameters 
given the care we have taken to minimise sources of systematic errors. }
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
The average value $\langle m_{\rm sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm e,sph} \rangle$ from all fits to a galaxy, 
not to be confused with the mean effective surface brightness within $R_{\rm e,sph}$, is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{IC 1459: 
  An elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and indications of a nuclear stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic2560_1Dfit.eps}
  \caption{IC 2560: A barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
  and dust within the central $2''.5$ \citep{martini2003}.
  A visual inspection of the image of IC 2560 reveals a boxy bulge and
  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
  The disk appears to be slightly lopsided along the direction of the bar,
  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
  This is why the surface brightness profile deviates from a perfect exponential
  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which is excluded from the fit.
  Motivated by the presence of a strong optical AGN and dust in the nucleus (which adds rather than obscures at $3.6\rm~\mu m$), 
  we account for an excess of non-stellar light by adding a central Gaussian component to the model.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic4296_1Dfit.eps}
  \caption{IC 4296:
  An elliptical galaxy. 
  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  After masking the innermost $6''.1$, 
  we find that a single S\'ersic profile provides a good description of this galaxy.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m31_1Dfit.eps}
  \caption{M31 (Andromeda galaxy):
  A spiral galaxy. 
  Although for decades this galaxy had been classified as an unbarred spiral,
  recent works have revealed the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}, 
  seen as the plateau at $800'' \lesssim R_{\rm maj} \lesssim 1000''$.
  M31 also features a broad ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, is excluded from the fit.
  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
  The addition of a Ferrer function to account for the bar notably improves the fit.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m49_1Dfit.eps}
  \caption{M49:
  The brightest member of the Virgo cluster, a giant elliptical galaxy 
  with a slightly resolved partially depleted core \citep{rusli2013}.  %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
  The data within the innermost $12''$ are excluded from the fit.
  We fit M49 with a single S\'ersic profile. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{M59:
  An elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
  the velocity map (ATLAS$^{\rm 3D}$) confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1316_1Dfit.eps}
  \caption{NGC 1316:  
  A merger. 
  The galaxy is composed of a bulge, an elongated structure that can be identified with a bar, 
  two obvious rings, an outer exponential disk or halo, and a bright nuclear component. }
  \end{center}
  \end{figure}

>>>>

\author{Giulia A. D. Savorgnan and Alister W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia}
\email{gsavorgn@astro.swin.edu.au}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{m49nooverlap.eps}
\includegraphics[width=0.49\columnwidth]{m49overlap.eps}
\caption{Example of the \emph{overlap} correction. 
The image mosaic of the galaxy M49 was obtained by co-adding frames coming from 8 different AORs.
The evident patchiness (left image) was removed (right image) using the \emph{overlap} module.}
\label{fig:overlap}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\columnwidth]{n4459brightstar.eps}
\includegraphics[width=0.49\columnwidth]{n4459nobrightstar.eps}
\caption{Example of aestethic correction.
The images show the mosaic of the galaxy NGC 4459 before (left) and after (right) the partial removal 
of a bright saturated star.}
\label{fig:aesth}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{psf.eps}
%\includegraphics[width=1\columnwidth]{star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{n3377_1Dfit.eps}
%\caption{the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

\begin{figure*}[h]
\begin{center}
\includegraphics[width=\fitfigurewidth]{n2974_1Dfit.eps}
\caption{Best-fit model, and isophotal parameters, for the galaxy NGC 2974. 
The left panels refer to the major-axis $R_{\rm maj}$, 
while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
The black points are the observed data.  
The color lines represent the individual (PSF-convolved) model components:
red=S\'ersic (bulge), dark blue=exponential (disk), green=Gaussian (AGN), cyan=Ferrer (bar), gray=Gaussian ring (ring). 
The best-fit parameters for the S\'ersic bulge model are inset.
The total (PSF-convolved) model is shown with a black dashed line, 
but it is hard to distinguish because it almost perfectly matches the data, 
hence the residual profile is additionally shown as $\Delta \mu$ in the second row.
The horizontal grey dashed line corresponds to an intensity 
equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. 
Such profiles are available online for all other galaxies successfully modelled in 1D (see Table \ref{tab:fitres}).}
\label{fig:n2974ex}
\end{center}
\end{figure*}

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{m59_1Dfit.eps}
%\caption{the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{n1332_1Dfit.eps}
%\caption{the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{n2974_imgmsk.eps}
\includegraphics[width=\columnwidth]{n2974_unsharp.eps}
\includegraphics[width=\columnwidth]{n2974_model.eps}
\includegraphics[width=\columnwidth]{n2974_resid.eps}
\caption{Image of the galaxy NGC 2974 with its mask (top panel), unsharp mask (second panel), 
best-fit 2D model (third panel), 
and residual image after the subtraction of the 2D model (bottom panel).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{comparison_r_e.eps} 
\caption{2D versus 1D major-axis measurements of the spheroid effective radii. 
The dashed line displays the 1:1 relation.}
\label{fig:re1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{comparison_n.eps} 
\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.}
\label{fig:n1d2d}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{comparison_mag.eps} 
\caption{2D versus 1D measurements of the $3.6~\rm \mu m$ spheroid magnitudes. The dashed line displays the 1:1 relation.}
\label{fig:mag1d2d}
\end{center}
\end{figure}

@@

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{comparison_all_n.eps} 
\caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
Each data point corresponds to an individual measurement from: 
\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
Black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to the measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively, 
corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres} (see Section \ref{sec:err} for details).
We consider these to be absolute upper limits to the uncertainty on our parameters 
given the care we have taken to minimise sources of systematic errors. }
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{comparison_all_r_e.eps} 
\caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{comparison_all_mag_sph.eps} 
\caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
The average value $\langle m_{\rm sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{comparison_all_mu_e.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm e,sph} \rangle$ from all fits to a galaxy, 
not to be confused with the mean effective surface brightness within $R_{\rm e,sph}$, is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{comparison_all_mu_0.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{ic1459_1Dfit.eps}
  \caption{IC 1459: 
  An elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and indications of a nuclear stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{ic2560_1Dfit.eps}
  \caption{IC 2560: A barred spiral galaxy with a Seyfert AGN \citep{veroncettyveron2006}
  and dust within the central $2''.5$ \citep{martini2003}.
  A visual inspection of the image of IC 2560 reveals a boxy bulge and
  a large scale bar that extends out to $R_{\rm maj} \lesssim 43''$.
  The disk appears to be slightly lopsided along the direction of the bar,
  due to two non-symmetric ansae, but it becomes symmetric beyond $R_{\rm maj} \gtrsim 60''$. 
  This is why the surface brightness profile deviates from a perfect exponential
  in the radial range $42'' \lesssim R_{\rm maj} \lesssim 60''$, which is excluded from the fit.
  Motivated by the presence of a strong optical AGN and dust in the nucleus (which adds rather than obscures at $3.6\rm~\mu m$), 
  we account for an excess of non-stellar light by adding a central Gaussian component to the model.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{ic4296_1Dfit.eps}
  \caption{IC 4296:
  An elliptical galaxy. 
  Due to its high stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  After masking the innermost $6''.1$, 
  we find that a single S\'ersic profile provides a good description of this galaxy.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{m31_1Dfit.eps}
  \caption{M31 (Andromeda galaxy):
  A spiral galaxy. 
  Although for decades this galaxy had been classified as an unbarred spiral,
  recent works have revealed the presence of a bar \citep{athanassoulabeaton2006m31,beaton2007m31,morrison2011m31}, 
  seen as the plateau at $800'' \lesssim R_{\rm maj} \lesssim 1000''$.
  M31 also features a broad ring-like structure at $R_{\rm maj} \sim 50'$ \citep{athanassoulabeaton2006m31}. 
  We applied the \emph{smoothing} technique described in Section \ref{sec:smooth} to the analysis of M31.
  The region $2000'' \lesssim R_{\rm maj} \lesssim 3400''$, where the pseudo-ring is observed, is excluded from the fit.
  A S\'ersic + exponential fit is not adequate to describe the light profile of M31,
  as the residuals of such fit display a structure in correspondence of the bar ($R_{\rm maj} \lesssim 1500''$).
  The addition of a Ferrer function to account for the bar notably improves the fit.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{m49_1Dfit.eps}
  \caption{M49:
  The brightest member of the Virgo cluster, a giant elliptical galaxy 
  with a slightly resolved partially depleted core \citep{rusli2013}.  %($R_{\rm break} = 1''.8$, \citealt{rusli2013}).
  The data within the innermost $12''$ are excluded from the fit.
  We fit M49 with a single S\'ersic profile. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{m59_1Dfit.eps}
  \caption{M59:
  An elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
  the velocity map (ATLAS$^{\rm 3D}$) confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{n1316_1Dfit.eps}
  \caption{NGC 1316:  
  A merger. 
  The galaxy is composed of a bulge, an elongated structure that can be identified with a bar, 
  two obvious rings, an outer exponential disk or halo, and a bright nuclear component. }
  \end{center}
  \end{figure}
